% Put your abstract here

\begin{abstractwithpageno}	
The Armed Forces and Police Mutual Benefit Association Incorporated (AFPMBAI) currently struggles with an inefficient and insecure document management system. Sensitive Board of Trustees records are scattered across Google Drive, local storage, and on-premise servers, creating vulnerabilities. This study tackles this problem by creating a secure, central knowledge system: the AI-Assisted Board of Trustees Document Archiving System. It's built for on-premise use to keep all data under AFPMBAI's control and meet compliance rules.

Using an Agile approach, the project incorporated Docling for structured metadata extraction and a locally hosted Gemma 3:1B Large Language Model (LLM) through Ollama. This setup allows for natural language searches that understand context, using a Retrieval-Augmented Generation (RAG) framework. System security was strengthened with AES-256 encryption, role-based access control (RBAC), and thorough audit trails.

User Acceptance Testing (UAT) showed a 100\% pass rate in the final version. An 8-hour stress test proved very reliable, with no errors across 39,949 requests. The system earned an "Excellent" APDEX score of 0.962, drastically cutting down the time it takes to find documents compared to old manual methods. These results show that secure, smart archiving systems can be successfully implemented in cautious, security-focused settings to improve how things run and preserve institutional knowledge.
\end{abstractwithpageno}