% Put the future works here

\section{FUTURE WORK}
    Improving this system is an ongoing effort. The current AI-Assisted Board of Trustees Document Archiving System for AFPMBAI already excels at secure document extraction and search, but there's potential for further enhancements. A key future upgrade involves the system's hardware.

Currently, the system operates on a server running Windows Server 2019 Datacenter, equipped with two Intel Xeon (Icelake) processors (6 cores each) and 128 GB of RAM. While this configuration handles file storage and organization effectively, the AI's processing can be slow as it relies solely on the Central Processing Units (CPUs). To address this, I suggest adding a dedicated Graphics Processing Unit (GPU). A GPU would enable the system to perform many tasks simultaneously through parallel processing which increasingly speed up AI responses and prevent slowdowns as more documents are added.

Beyond hardware, future versions could incorporate better document management features such as automated retention policies and digital approval workflows for board members. I also intend to refine how the AI interprets specialized professional language. By training the AI on legal and financial terms specific to AFPMBAI, it will become much more precise at analyzing complex policy documents.

Ultimately, the system could be expanded to automatically summarize board meetings and generate dashboards that highlight trends in decision-making over time. These updates would transform the system from a basic search tool into an intelligent assistant that helps leaders make more informed choices. While the current system provides a solid and secure foundation, adding a GPU and sharpening the AI's capabilities will ensure it delivers even greater benefit to the organization in the long term.