% Put the summary and conclusion here

\section{SUMMARY AND CONCLUSION}
    This study describes the AI-Assisted Board of Trustees Document Archiving System, built for the Armed Forces and Police Mutual Benefit Association Incorporated (AFPMBAI). The project tackled the challenges of handling, finding, and protecting board documents within a secure, on-premise setup. The main goal was to turn traditional document archiving into a smart, searchable, and secure knowledge system without using outside cloud services.

    The system uses the Docling library to pull structured text and information from uploaded documents. This allows for precise indexing and organized AI processing later on. We also included Gemma 3, a free, open-source Large Language Model, run locally using Ollama. A Retrieval Augmented Generation (RAG) pipeline lets users ask questions about memorandums, meeting minutes, and board resolutions, keeping the information within its original context while maintaining strict control over the data.

    This project shows that secure, organization-wide AI tools can be built with open technologies without risking privacy. The system keeps sensitive institutional data safe within AFPMBAI’s controlled environment through AES-256 encryption, strict checks, and Role-Based Access Control (RBAC).

    The results confirm that adding AI to document archiving greatly improves how quickly information can be found, lessens the need for manual searching, and improves the organization's collective memory. Crucially, the project provides a useful and repeatable model for using AI in organizations focused on governance that value security, control, and following rules. The AI-Assisted Document Archiving System is therefore not just a technical improvement but also a smart move towards organized and responsible digital change within AFPMBAI.